Lobbying and Legislative Uncertainty

### 2016-05-10 presentation.tex
make corrections from Wallis talk

\documentclass{beamer} 
%\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

\subsection{Simultaneous Model}
\begin{frame}{What I know...}
\pause
FOCs look the same for Vote Buyer B, e.g.
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item Either one root at zero, or
			\pause
			\item Two roots and only larger one (at $X>0$?) satisfies SOC
		\end{itemize}

\vskip.1in
\pause
For Vote Buyer A,
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{1}{\left(1+e^{-X}\right)^2}= \frac{1}{W_A}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item One root: zero or $X<0$
		\end{itemize}

@@

\begin{frame}{Next Steps}
\pause
\begin{itemize}[<+->]
	\item Modify model so that both legislators can lobby the \textit{same} legislator in equilibrium
	\item Derive tight identification of empirical estimates from structural model
	\item Provide micro-founded explanations for the variation in uncertainty that lobbies face
\end{itemize}

>>>>

%\documentclass{beamer} 
\documentclass[handout]{beamer} 
\usetheme{Ilmenau}
\usepackage{graphicx,verbatim,hyperref}
\usepackage{textpos}

@@

\subsection{Simultaneous Model}
\begin{frame}{What I know...}
\pause
FOC look the same for Vote Buyer B, e.g. for $b(0)$:
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_B}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item Either one root at zero, or
			\pause
			\item Two roots and only larger one (at $X>0$?) satisfies SOC
		\end{itemize}

\vskip.1in
\pause
For Vote Buyer A, FOC for $a(0)$:
\pause
	\[
		\frac{e^{-Y} + e^{-Z}}{\left(1+e^{-Y}\right)\left(1+e^{-Z}\right)} \frac{e^{-X}}{\left(1+e^{-X}\right)^2}= \frac{1}{W_A}
	\]
	\vskip-.15in
	\pause
		\begin{itemize}
			\item Similar to $B$, except only smaller root satisfies SOC
		\end{itemize}

@@

\begin{frame}{Next Steps}
\pause
\begin{itemize}[<+->]
	\item Modify model so that both vote buyers can lobby the \textit{same} legislator in equilibrium
	\item Derive tight identification of empirical estimates from structural model
	\item Provide micro-founded explanations for the variation in uncertainty that lobbies face
\end{itemize}
